### 2015-01-12 etc/abstract.tex
abstract

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Choosing a
smaller subset of mutations to run is a simple approach that can
alleviate this problem.  Mutation operator selection has been heavily
researched. Recently, researchers have found that sampling mutants can
achieve accuracy and mutant reduction similar to operator selection.
%
%2.Saywhyit’saninterestingproblem
However, the empirical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
% that can be drawn from the previous
%research has been limited due to the small number of subject programs. Further,
%which sampling technique is best is still an open problem that needs to be
%tackled on a much larger range of test subjects.

%3.Saywhatyoursolutionachieves

Our research compares a large number of sampling and operator
selection criteria based on their ability to predict the full mutation
score as well as the consistency of mutation reduction ratios
achieved. Our results can be used to choose an appropriate mutation
reduction technique by the reduction and level of fidelity to full
mutation results required.

@@

We find that all sampling approaches perform better than operator
selection methods, when considering ability to predict the full
mutation score as well as the consistency of mutation reduction ratios
achieved.

>>>>

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Choosing a
smaller subset of mutations to run is a simple approach that can
alleviate this problem.  Mutation operator selection has been heavily
researched. Recently, researchers have found that sampling mutants can
achieve accuracy and mutant reduction similar to operator selection.
Newer research has also indicated that program element based sampling
may be better than pure random sampling or traditional operator selection.

%
%2.Saywhyit’saninterestingproblem
However, the empirical support for these conclusions has been limited,
due to the small number of subject programs investigated. The best sampling
technique is also an open problem. Further, current research has focused
on evaluating mutation analysis techniques over adequate test suites. However,
real world test suites are often far from test adequacy, and it is not clear
if the results carry over to non-adequate test suites.
%3.Saywhatyoursolutionachieves

We propose that a better mutation selection criteria should generate a larger
number of defective behaviors than a worse mutation selection criteria, which
we judge using the number of non-redundant tests able to kill the sampled
mutants.

We evaluate the performance of various selection criteria on 250 opensource
projects from github, which shows that the popular operator selection and
element based sampling are not much better than random selection, and often
performs worse than random selection. This suggests a need for further research
on better methods of operator selection and sampling.

% Our results can be used to choose an appropriate mutation
% reduction technique by the reduction and level of fidelity to full
% mutation results required.

@@

% We find that all sampling approaches perform better than operator
% selection methods, when considering ability to predict the full
% mutation score as well as the consistency of mutation reduction ratios
% achieved.
